---
title: "Report of advanced Bland Altman-analysis"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  # html_notebook: default
  html_document:
    df_print: paged
    number_sections : true
    toc : true
  word_document:
    toc : true
  md_document: 
    toc : true
  pdf_document:
    number_sections : true
    toc : true
params:
  tab: tab
  fig: fig
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
options(knitr.kable.NA = ' ')
```

# Input parameters and 'tau'
```{r, results="asis"}
knitr::kable(params$tab$input_param, format = 'markdown', digits = 3)
```
Table: Input parameters

# Main results of advanced Bland Altman-analysis
```{r, results="asis"}
knitr::kable(params$tab$analysis_results_m, format = 'markdown', digits = 7)
```
Table: Main results of advanced Bland Altman-analysis 
(SD: standard deviation, SE: standard error, LoA: limit of agreement, 
CI: confidence interval, BT: using bootstrapping, 
BA: using method of Bland Altman)

```{r, echo=FALSE}
  params$fig$plot_res
```
Figure: Bland Altman-plot
(LoA: limit of agreement, CI: confidence interval (MOVER))

# Main results of advanced, modified Bland Altman-analysis
```{r, results="asis"}
knitr::kable(params$tab$analysis_results_mod_m, format = 'markdown', digits = 7)
```
Table: Main results of advanced modified Bland Altman-analysis
(SD: standard deviation, SE: standard error, LoA: limit of agreement, 
CI: confidence interval, BT: using bootstrapping, 
BA: using method of Bland Altman)

```{r, echo=FALSE}
  params$fig$plot_res_mod
```
Figure: Bland Altman-plot (modified analysis)
(LoA: limit of agreement, CI: confidence interval (MOVER))


# Parameters for calculation of repeatability coefficients
```{r, results="asis"}
knitr::kable(params$tab$param_rep_coeff_m, format = 'markdown', digits = 7)
```
Table: Parameters for calculation of repeatability coefficients

Repeatability coefficients for 95% of the subjects can be calculated as 
$1.96 \cdot \sqrt2 \cdot SX$/ $1.96 \cdot \sqrt2 \cdot SY$. Be careful when 
using it for analysis with varying true value (for more information please see:
Bland, J. M. & Altman, D. G., "Measuring agreement in method comparison
studies", Statistical methods in medical research, 8 (2), 1999.
DOI: 10.1177/096228029900800204).

# QQ-plot of residuals
```{r, echo=FALSE}
  params$fig$qq_resid
```
Figure: QQ-plot of residuals

# QQ-plot of individual means of differences
```{r, echo=FALSE}
  params$fig$qq_ind_means
```
Figure:  QQ-plot of individual means of differences

# Plot of the residuals vs means of each measurement
```{r, echo=FALSE}
  params$fig$plot_res_means
```
Figure: Plot of the residuals vs means of each measurement

# Plot of the residuals vs subject ID
```{r, echo=FALSE}
  params$fig$plot_res_id
```
Figure: Plot of the residuals vs subject ID

# Individual means of differences
```{r, results="asis"}
knitr::kable(params$tab$ind_means, format = 'markdown', digits = 7)
```
Table: Individual mean of differences and number of measurements of each subject

# Residuals
```{r, results="asis"}
knitr::kable(params$tab$resid, format = 'markdown', digits = 7)
```
Table: Residuals

# Input data
```{r, results="asis"}
knitr::kable(params$tab$input_data, format = 'markdown', digits = 7)
```
Table: Input data
