---
title: "Report of modified Bland Altman-analysis"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  # html_notebook: default
  html_document:
    df_print: paged
    number_sections : true
    toc : true
  word_document:
    toc : true
  md_document: 
    toc : true
  pdf_document:
    number_sections : true
    toc : true
params:
  tab: tab
  fig: fig
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
options(knitr.kable.NA = '-')
```

# Input parameters
```{r, results="asis"}
kable(params$tab$input_param_m, format = 'markdown', digits = 7)
```
Table: Input parameters

# Analysis results
```{r, results="asis"}
kable(params$tab$analysis_results_m, format = 'markdown', digits = 7)
```
Table: Analysis results

```{r, echo=FALSE}
  params$fig$plot_res
```
Figure: Plot of analysis results

# Analysis results (modified)
```{r, results="asis"}
kable(params$tab$analysis_results_mod_m, format = 'markdown', digits = 7)
```
Table: Analysis results (modified)

```{r, echo=FALSE}
  params$fig$plot_res_mod
```
Figure: Plot of analysis results (modified)

# Repeatability coefficients
```{r, results="asis"}
kable(params$tab$rep_coeff_m, format = 'markdown', digits = 7)
```
Table: Repeatability coefficients

# QQ-plot of residuals
```{r, echo=FALSE}
  params$fig$qq_resid
```
Figure: QQ-plot of residuals

# QQ-plot of individual means
```{r, echo=FALSE}
  params$fig$qq_ind_means
```
Figure: QQ-plot of individual means

# Plot of the residuals vs mean
```{r, echo=FALSE}
  params$fig$plot_res_means
```
Figure: Plot of the residuals vs mean

# Plot of the residuals vs ID
```{r, echo=FALSE}
  params$fig$plot_res_id
```
Figure: Plot of the residuals vs ID

# Individual means of differences
```{r, results="asis"}
kable(params$tab$ind_means, format = 'markdown', digits = 7)
```
Table: Individual means

# Residuals
```{r, results="asis"}
kable(params$tab$resid, format = 'markdown', digits = 7)
```
Table: Residuals

# Input data
```{r, results="asis"}
kable(params$tab$input_data, format = 'markdown', digits = 7)
```
Table: Input data
